---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# astho.viz

<!-- badges: start -->
```{r}
library(usethis)
use_lifecycle_badge("stable")
```

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->

A data visualization package to generate themed, accessible highcharter visualizations using an ASTHO theme.

## Installation

You can install the development version of astho.viz from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lindsayjorgenson/astho.viz")
```

## Example

Create a categorical map.

```{r example}
library(astho.viz)

categorical_map(data = astho_governance,
                fips_column = "fips",
                selected_value = "governance",
                title_text = 
                  "Governance of State and Island Area Public Health Agencies", 
                subtitle_text = "2022", # content under the title
                caption_text =
                  "<b> Source: </b> Association of State and Territorial Health 
                  Officials.ASTHO Profile of State and Territorial Public Health, 
                  Volume Six. Arlington, VA: Association of State and 
                Territorial Health Officials. 2023.",
                accessible_desc =
                  "This is a map of governance classification, with most 
                  jurisdictions classified as decentralized followed by 
                  centralized. Few jurisdictions have mixed or shared 
                  governance. Enter the map to review classification at the 
                  jurisdiction level.",
                my_tooltip = "<b>{point.JurisdictionName}</b><br> {point.value}",
)
```

## Next

We will soon add additional geographic maps, tile maps, bar charts, line graphs,
and pie charts all customized with the ASTHO theme.
